### 2020-04-23 paper.tex
Rephrase

Various ways of implementing reactive applications emerged over time. The Observer design pattern \cite{observerDesignPattern}, originated in Object Oriented Programming \emph{(OOP)}, is a basic pattern we can find in many of todays API implementations providing reactivity \cite{ownPaper}. Functional Programming \emph{(FP)} experiments with reactive language extensions like the on animations specialized library Fran (Haskell) \cite{SurveyOnReactiveProgramming} or more recently the reactive runtime and DSL REScala (Scala) \cite{10.1145/2577080.2577083}. The declarative nature of FP lead finally to what we understand as ``Reactive Programming'' today.

>>>>

Various ways of implementing reactive applications emerged over time. The Observer design pattern \cite{observerDesignPattern}, originated in Object Oriented Programming \emph{(OOP)}, is a basic pattern we can find in many of todays API implementations \cite{ownPaper}. Functional Programming \emph{(FP)} shines with specific reactive language extensions like Fran (Haskell) \cite{SurveyOnReactiveProgramming} or more recently REScala (Scala) \cite{10.1145/2577080.2577083}. The declarativeness of FP finally lead to what we understand under ``Reactive Programming'' today.
